---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# motifator

The goal of motifator is to allow users to generate spatial motifs that replicate the ones seen in real-world data, without including any potentially identifying information.

## Installation

You can install motifator from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jzelner/motifator")
```

## Example

Consider this example: You want to compare the impact of spatial clustering of different levels of vaccination coverage in a model of infectious disease transmission. So, let's make a map where we assume that about 50% of the population is vaccinated, but there is no spatial clustering.

Our metric of spatial clustering for this example is Moran's I. Theoretical values of I run from -1 to 1. I = -1 implies *anticorrelation*, in which neighboring cells have values that are maximally different from each other. By contrast, values closer to +1 indicate strong spatial *autocorrelation*. 

Let's sample a map with strong spatial correlation:

```{r example}
require(motifator)
m <- sampleProportion(10, i_target = 0.9, mean_target = 0.5)
plotMap(m)
```

Now for comparison, let's do the same thing but for a `10 x 10` map with no spatial structure and the same mean:

```{r example2}
require(motifator)
m <- sampleProportion(10, i_target = 0.0, mean_target = 0.5)
plotMap(m)
```

